\documentclass{../tex/report}
\usepackage{setspace} % Setting line spacing
\usepackage{ulem} % Underline
\usepackage{caption} % Captioning figures
\usepackage{subcaption} % Subfigures
\usepackage{geometry} % Page layout
\usepackage{multicol} % Columned pages
\usepackage{array,etoolbox}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage[toc,page]{appendix}
\setlist{noitemsep}

%READ THIS:
%mark comments with OpenComment or ClosedComment as you write, so we can ctrl+f as needed.

% Page layout (margins, size, line spacing)
\geometry{letterpaper, left=1in, right=1in, bottom=1in, top=1in}
\setstretch{1}

% Headers
\pagestyle{fancy}
\lhead{PeaPod - Design Report}
\rhead{PeaPod Technologies Inc.}

\begin{document}

\begin{titlepage}
    \begin{center}
        \vspace*{1.2cm}

        \textbf{\large{PeaPod - Design Report}}

        \vspace{0.5cm}

        Primary Written Deliverable for the Deep Space Food Challenge Phase 1

        \vfill
        \input{../tex/Namecard.tex}
        \vspace{.75cm}

        Revision 1.1\\
        PeaPod Technologies Inc.\\
        January 31st, 2023

    \end{center}
\end{titlepage}

\thispagestyle{plain}

\tableofcontents
\newpage

\section{Design Abstract}
\textbf{Prompt}: \textit{Please provide a brief summary description of your proposed food production technology within a 1,500 character limit. The abstract may answer some of the following questions: What is your proposed solution? What is novel, sustainable, and innovative about your proposed solution? What types of food does your solution create? How are you minimizing inputs and maximizing food outputs?}

\input{../tex/report/Abstract.tex}

\uline{\textbf{1498 Characters} (2 under)}

\newpage

\section{Design Report}

\subsection{Description}
\label{sec:description}

\subsubsection{Part A}
\label{sec:description-a}

\textbf{Prompt}: \textit{Please provide a more fulsome description of your food production technology. Your description needs to include information about what the technology is, what it does, how it functions, and how the crew will interact with it. Be sure to also provide any descriptions of major hardware components and processes in relation to your technology.}

\input{../tex/report/Description.tex}

\uline{\textbf{2881 Characters} (119 under)}

\vspace{0.5cm}

\subsubsection{Part B}
\label{sec:description-b}

\textbf{Prompt}: \textit{Please describe the basic operations concept of the food production technology. In your response, describe assumptions required of operation. You can also include, for example, details about whether a sterile/aseptic environment is needed, if special steps are required between production cycles, or if fluids or materials must be removed or added to prime/inoculate a system.}

\input{../tex/report/Operations.tex}

\uline{\textbf{1479 Characters} (21 under)}

\newpage

\subsection{Innovation}
\label{sec:innovation}

\textbf{Prompt}: \textit{This question seeks to establish an understanding of how your technology is different from other technologies that currently exist. Your description needs to be clear and well defined using simple language when detailing how your food production technology is novel, innovative and sustainable. Ensure to provide examples that will portray the novelty of your technology.}

\input{../tex/report/Innovation.tex}

\uline{\textbf{2958 Characters} (42 under)}

\vspace{0.5cm}

\subsection{Adherence to Constraints}
\label{sec:constraints}

\textbf{Note}: \textit{Whether in space or in a remote community on Earth, there are several constraints that your food production technology should adhere to. This question outlines key constraints below that your technology will need to address. In Phase 1, Adherence to Constraints is not meant to determine whether the Design Report itself is complete in including all the required information. This question is meant to ensure that Teams have considered the constraints, and that the food production technology design, at a minimum, falls within those constraints. In future Phases, Teams’ food production technologies will be evaluated and scored on whether or not the design stays within the constraints so that it ultimately can meet CSA’s needs and deliver value.}

\subsubsection{Outer Dimensions, Volume}
\label{sec:constraints-volume}

\textbf{Constraint}: \textit{Fits through 1.07m x 1.90m doorway; W < 1.820m, D < 2.438m, H < 2.591m; V<= 2m${}^3$}

% 300chars

% PeaPod is a modular system of "unit cells," each consisting of a .5 x .5 x .5 meter cube frame with insertable insulation panels. This cell is expandable to physically link with neighbouring cells, creating a single frame. An "expanded system" may share a single control module and have no separating wall (thus producing the same environment), or may have multiple control modules operating in either a master-slave topology (again, producing a homogenous system with no separation) or may be linked only physically (having no sharing of environment or control). The adaptability of PeaPod ensures it meets the constraints of its environment while yielding as much produce as possible.

\textbf{Standard Expanded PeaPod}: 4x3x1 units (0.5m on all sides) + control module = 2m wide x 1.7m tall x .5m deep = 1.5m${}^3$ (< 2)

With width treated as depth for the purposes of the considerations of the "room size" constraint, the Standard meets this constraint.

\uline{\textbf{270 Characters} (30 under)}

\vspace{0.5cm}

\subsubsection{Power Consumption}
\label{sec:constraints-power}

\textbf{Constraint}: \textit{Avg < 1500 W, Peak < 3000 W}

For calculations and justification, see preliminary calculations Appendix \ref{app:power}.

\textbf{Total Power Consumption}: 1,284W

\uline{\textbf{98 Characters} (202 under)}

\newpage

\subsubsection{Water Consumption}
\label{sec:constraints-water}

\textbf{Unconstrained}

For calculations and justification, see preliminary calculations Appendix \ref{app:water}.

\textit{Humidification}: CNet = \textbf{500mL initial + 50mL per hour}

\textit{Aeroponics}: CNet = \textbf{1.25L primed + 1.2L per hour}.

\uline{\textbf{171 Characters} (129 under)}

\vspace{0.5cm}

\subsubsection{Mass} 
\label{sec:constraints-mass}

\textbf{Unconstrained}

For part breakdown, calculations, and justification, see preliminary calculations Appendix \ref{app:mass}.

Total: \textbf{70kg}

\uline{\textbf{83 Characters} (217 under)}

\vspace{0.5cm}

\subsubsection{Data Connection} 
\label{sec:constraints-data}

\textbf{Unconstrained}

% \textit{Automation}: All of PeaPod's operation is automated, save for a select few setup, maintenance, and harvest tasks. This is controlled by a central computer, which uses a "program" to enact the desired environment at each point in time throughout the plant life cycle. 
\textit{Remote Control}: The program may be changed \uline{instantaneously} as an \textbf{appended instruction set} with immediate effect.
% \textit{Feedback}: The feedback sensors provide the computer with information that will influence the control it exerts. For example, if the program indicates the leaf zone temperature should be set to 22 degrees C, the computer would apply greater power to the heater if the current temperature was 18 degrees C as opposed to 21 degrees C. This forms a control loop for each parameter, relying on one of many control functions (bang-bang, PID, etc.).

\textit{Data Presentation}: Plant and environment data can be viewed with \uline{live updates and video feed}.

\uline{\textbf{206 Characters} (94 under)}

\vspace{0.5cm}

\subsubsection{Crew Time Requirement - Setup \& Maintenance}
\label{sec:constraints-crewtime} 

\textbf{Constraint}: \textit{4 hrs/week}

For calculations and justification, see preliminary calculations Appendix.

Total setup process time (2 trays per unit, 12 units, 1 CM): \textbf{17.5 hours} (\textit{one person}) or \textbf{4.5 hours} (\textit{crew of 4})

Total maintenance time per week: \textbf{1-2 hours} (depending on program)

\uline{\textbf{246 Characters} (54 under)}

\newpage

\subsubsection{Palatability of Crop Output} 
\label{sec:constraints-palatability}

\textbf{Constraint}: \textit{>= 6.0 Hedonic}

Hydroponic crops have seen commercial success \cite{commercialhydro}, suggesting that their output is of sufficient hedonic quality to be desired.

\textit{Case Study in Fresh Produce}: Acceptability of Fresh Cantaloupe Melon \cite{melon}

\begin{itemize}
    \item Appearance: 7.93/9.00
    \item Aroma: 7.77/9.00
    \item Flavor: 6.83/9.00
    \item Texture: 7.43/9.00
    \item \textbf{Overall}: 7.17/9.00 (>6.00)
\end{itemize}

\uline{\textbf{292 Characters} (8 under)}

\vspace{0.5cm}

\subsubsection{Operational Constraints} 
\label{sec:constraints-operational}

\textbf{Constraint}: \textit{Terrestrial: gravity (9.81 m/s${}^2$), ambient atmospheric pressure (101,325 Pa), ambient atmospheric temperature (22 °C), ambient atmospheric humidity (50 \%RH)}

Design operates in terrestrial conditions.

Ambient pressure: tank, bladder, and nozzle are designed to produce indicated outputs at standard air pressure
Ambient temperature and humidity: less concern, housing is sealed and insulated

\uline{\textbf{231 Characters} (69 under)}

\newpage

\subsection{Performance Criteria}

\textbf{Note}: \textit{This section seeks to understand how the proposed food production technology addresses the performance criteria of the Challenge. Describe how the food production technology addresses the following performance criteria.}

\subsubsection{Acceptability}
\label{sec:acceptability}

\textbf{Acceptability of Process}
\label{sec:acceptability-process}

\textbf{Prompt}: \textit{Describe in detail the processes and procedures of using your technology. Please also provide an assessment (using industry standards and/or existing research) that your technology processes are likely to be user friendly and acceptable to the crew.}

\textbf{Target:} \textit{The process must be something crew members could be expected to accomplish in a reasonable amount of time, on a daily basis in a small kitchen-like space after a busy workday. Teams should consider the current target for Astronauts is 1 hour per meal (30 minutes for preparation, 30 minutes for the meal itself).}

% 3000chars

\input{../tex/report/AcceptabilityProcess.tex}

\uline{\textbf{2765 Characters} (235 under)}

\newpage

\textbf{Acceptability of Food Products}
\label{sec:acceptability-products}

\textbf{Prompt}: \textit{Please provide an assessment (using industry standards and existing research) that the food outputs of your technology are likely to meet the acceptability target. Rate and describe the potential acceptability of your food products on a 9 point hedonic scale in terms of appearance, aroma, flavor, and texture. The hedonic scale is a quantitative method that is accepted throughout the food science industry as a means to determine acceptability.}

\textbf{Target}: \textit{A food item measuring an overall acceptability rating of 6.0 or better on a 9-point hedonic scale for the duration of the mission is considered acceptable.}

% 3000chars

\input{../tex/report/AcceptabilityProducts.tex}

\uline{\textbf{1330 Characters} (1670 under)}

% Optional - Additional comments
% This additional text box with a 1,000 character limit allows you to provide any other information on acceptability and palatability you would like to submit to the Judging Panel.

\newpage

\subsubsection{Safety}
\label{sec:safety}

\textbf{Note}: \textit{The overall safety of the food production process and the food products are a top priority for this Challenge. No pathogens are permitted to exist within the food technology or its outputs.  Teams must take this into account in their Phase 1 designs. Designs that fail to account for pathogens will receive a "fail" score on the Safety category.}

\textbf{Safety of Process}
\label{sec:safety-process}

\textbf{Prompt}: \textit{Your answer will need to describe the safety associated with the food production process using your technology. The food production process includes: the safety of the food handling or processing procedures and environmental safety. Please include all food safety procedures that need to be followed.}

\textbf{Targets:}
\begin{itemize}
    \item Avoidance of hazardous compounds or materials used or produced (e.g., microbes, off-gassing, toxic components);
    \item Avoidance of hazards associated with cleaning this technology prior to and/or after use;
    \item Avoidance of physical, chemical, or biological hazards associated with the hardware or the process;
    \item No pathogens (i.e. nitrogen fixing bacteria); all nutrients provided directly;
    \item Clear mitigation strategies to address the aforementioned risks;
\end{itemize}

% 3000chars

\input{../tex/report/SafetyProcess.tex}

\uline{\textbf{2213 Characters} (787 under)}

\vspace{0.5cm}

\textbf{Safety of Food Products}
\label{sec:safety-products}

\textbf{Prompt}: \textit{Your answer will need to describe the safety of the resulting food products (outputs), including safety for repeated human consumption.}

\textbf{Target}: \textit{Consumption safety: Resulting food product is safe for repeated human consumption as defined by NASA-STD-3001 (see Reference Materials)}

% 3000chars

\input{../tex/report/SafetyProducts.tex}

\uline{\textbf{982 Characters} (2018 under)}

% Optional - Additional comments
% This additional text box with a 1,000 character limit allows you to provide any other information on the safety associated with the food production process using your technology.

\newpage

\subsubsection{Resource Inputs and Outputs}
\label{sec:resource}

\textbf{Note}: \textit{In your response, you will need to describe the resource requirements of the food production process (inputs) and all outputs. You will need to also include the estimated quantities of each input and output, as well as the nutritional quality of the food product.}

\textbf{Resource Inputs}
\label{sec:resource-inputs}

\textbf{Prompt}: \textit{Indicate the inputs needed to run your food production technology. Inputs may include: Raw materials, energy, water, or other materials that enter the system.}

% 3000chars

\input{../tex/report/Inputs.tex}

\uline{\textbf{755 Characters} (2245 under)}

\vspace{0.5cm}

\textbf{System Outputs}
\label{sec:resource-outputs}

\textbf{Prompt}: \textit{Indicate the outputs generated from your food production technology. }

% 3000chars

\input{../tex/report/Outputs.tex}

\uline{\textbf{535 Characters} (2465 under)}

\newpage

\textbf{Optimization}
\label{sec:resource-optimization}

\textbf{Prompt}: \textit{Provide a description on how the food production technology achieves the maximum amount of food output in relation to the quantity of inputs and quantity of waste output.} 

% 1500chars

\input{../tex/report/Optimization.tex}

\uline{\textbf{1479 Characters} (21 under)}

\vspace{0.5cm}

\textbf{Food Output Quality}
\label{sec:resource-outputquality}

\textbf{Prompt}: \textit{Please describe  the nutritional quality of the resulting food products from your technology. You will need to provide the nutritional potential of the food produced with your technology. Use values based on reasonable literature information that you can reference.}

\textbf{Targets:}
\begin{itemize}
    \item Maximum macronutrients supplied, as a percentage of a crewmember’s complete dietary needs;
    \item Maximum micronutrients supplied, as a percentage of a crewmember’s complete dietary needs;
    \item Maximum variety of nutrients supplied;
\end{itemize}

% 3000chars

Given the system can induce a wide and continuous range of environments, it can produce environments suitable for any aeroponically-growable crop. Within the 2 square meters allotted to the solution, 12 PeaPods can be placed in a Standard configuration, resulting in a hypothetical maximum of 4 different environments (4 vertical columns with 4 control modules). The sum of the plants grown can be any combination of any number of suitable plant species (grouped into the same environment if suitable, i.e. different microgreens together), and as such, can be selected to meet all macro and micro nutrient requirements (with fortification or supplementation of those nutrients not found in plants \cite{plantbased}). 

For example, quinoa - a crop already highly dense in nutrients (protein values up to 12-18\% of mass, unique amino acid composition high in lysine) - has shown excellent potential for hydroponic/aeroponic growth in controlled environments with increases in nutrient density and yield (up to 37\% harvest index, aka edible yield as a percentage of total mass). "Initial results indicate that quinoa could be an excellent crop for [controlled-environment agriculture] because of high concentration of protein ... and potential for greatly increased yields in controlled environments." \textit{NOTE}: Despite promising results, the experiment cited was performed with "no attempt to maximize productivity". When combined with the optimization routine, yields could be maximized even further \cite{quinoa}.

Other crops suitable to aeroponics are listed here alongside their benefits and some examples of nutrient analysis:
\begin{itemize}
    \item \textit{Microgreens} (sunflower sprouts, beansprouts, etc.) - Fast growth, edibility raw (minimal processing), more concentrated nutrients (9-40x higher than mature greens \cite{microgreens2}). High in a variety of vitamins and minerals \cite{microgreens1}.
    \item \textit{Legumes} (soybeans, chickpeas, etc.) - High caloric density. \textit{For 100g boiled soybeans}: 173 Calories. High in protein (16.6g), carbohydrates (9.9g) which are mostly fiber (6.0g), polyunsaturated fats (5.1g) and Omega-6 fatty acids (4.5g) \cite{soybeans}.
    \item \textit{Leafy Greens} (lettuce, spinach, cabbage, kale, etc.) - Fast growth (more bulk output, more filling), edibility raw (minimal processing), versatility. \textit{For 100g raw spinach}: 23 Calories. Contains protein (2.9g) and carbs (3.6g) which are mostly fiber (2.2g), as well as a variety of vitamins (A, C, K1, Bfolic acid) and minerals (iron, calcium) \cite{spinach}. 
\end{itemize}

These, in addition to herbs, berries, grains, garden produce, and root vegetables meet the vast majority of crew nutritional requirements.

\uline{\textbf{2429 Characters} (571 under)}

\vspace{0.5cm}

\textbf{Additional Comments}:

Let it be noted that the primary goal of this design is not to satisfy the nutrient or caloric constraints. It is of the opinion of the submission team after extensive study that there is no way to produce 10,000 Calories in a 2 cubic meter environment via crop growth. The closest we got was a method for the production of aeroponic minituber potatoes as described in \cite{minituber}, which produces an estimated 2,000 Calories per day in a 2 cubic meter space.

Instead, this system caters to the more "human" aspects of food - palatability and enjoyability, versatility of products for different cuisine, diversity of outputs, and the positive effects of growing plants on human emotional health, to name a few.

\uline{\textbf{715 Characters} (285 under)}

\newpage

\subsubsection{Reliability and/or Stability}

\textbf{Process Reliability}
\label{sec:reliability-process}

\textbf{Prompt}: \textit{Please provide a description of the reliability of your technology. Include operational lifespan, percentage functionality loss over 3 years, maintenance process, procedures, and schedule, including component maintenance/replacement and spare part requirements.}

\textbf{Target}: \textit{Less than 10\% loss of functionality or food production throughout a three-year mission.}

% 3000chars

%OpenComment pretty barebones, might need citations for material duration... feel free to add anything else that sells the reliability - NV
\input{../tex/report/ReliabilityProcess.tex}

\uline{\textbf{1341 Characters} (1659 under)}

% Scheduled maintenance breaks down to three primary tasks: refilling nutrients, cleaning spray nozzle, and harvesting/replacing plants.
% Since PeaPod mixes the nutrient solution automatically, the only required maintenance is replenshing stores of water and individual nutrients. By tracking consumption rates and using past trends, PeaPod can schedule the most efficient refill time in advance and notify the user.
% The spray nozzle, by way of its fine mesh, will build fine amounts of sediment over time. This can be easily cleaned by the user at either pre-determined times or, as mentioned above, when the unit detects an issue.
% Finally, plant harvesting is a quick task that simply constitues opening the unit and removing the plant. Replacing it only requires the user to open the unit, place the seed in the grow cup, and digitally set the grow conditions for PeaPod to follow.

\vspace{0.5cm}

\textbf{Input and Output Stability}
\label{sec:reliability-inputoutput}

\textbf{Prompt}: \textit{Provide a description of the stability of both the input products used and food product outputs. Include input and output shelf life, and degree of loss of quality over shelf life.}

\textbf{Target}: \textit{Longest possible shelf-life of the input and food products. They must remain safe, without any significant loss of nutritional value or quality at ambient conditions.}

% 1500chars

\input{../tex/report/Stability.tex}

\uline{\textbf{1171 Characters} (329 under)}

% Optional - Additional comments
% This additional text box with a 1,000 character limit allows you to provide any other information on reliability and stability you would like to submit to the Judging Panel.

\subsection{Terrestrial Potential}
\label{sec:terrestrial}

\textbf{Prompt}: \textit{Describe your vision of your food production technology’s potential to improve food production on Earth. Provide a concrete scenario in which your technology would serve the community in which it operates.}

% 3000chars

\input{../tex/report/TerrestrialPotential.tex}

\uline{\textbf{2987 Characters} (13 under)}

\newpage

\appendix

\begin{spacing}{0.5}
\small

\section{Preliminary Calculations}

\subsection{Power Usage Estimate}
\label{app:power}

The following estimate assumes "typical maximum" operating conditions, as this system is capable of producing far greater control than is necessary for the DSFC:
\begin{itemize}
    \item Thermoregulation at 25\% power for holding temperature;
    \item LEDs set to 20\% power (comparable to sunlight);
\end{itemize}

Estimate:
\begin{itemize}
    \item Automation Computer (Raspberry Pi) - \textbf{5W Average}
    \item Diaphragm Pump - \textbf{24W} 
    \item Lighting - 5 series x 3 LEDs/series x 9 boards/unit x 12 units x 3W/LED x 20\% power (typ.) = \textbf{972W}
    \item All Thermoregulation Peltier Tiles - 4 tiles per unit x 2 units (1 water + 1 air) x 8.5A x 15V x 25\% power (typ.) = \textbf{255W}
    \item Runoff Recycling Peristaltic Pump - \textbf{3W}
    \item All Sensors - \textbf{10W}
    \item All Fans - 10 fans (2+2 air thermo, 2 water thermo, 1+1 gas exchange, 2 humidification/dehumidification) x 2W per fan = \textbf{20W}
    \item Humidification Driver - \textbf{10W}
    \item Primary Aeroponic Solenoid - \textbf{5W}
\end{itemize}

\subsection{Water Usage Estimate}
\label{app:water}

\input{../tex/appendices/WaterUsage.tex}

\subsection{Mass Estimate}
\label{app:mass}

By using smaller parts, power consumption and complexity was reduced along with volume and mass. PeaPod's mass was also optimized through minimizing density across components. Aluminum was chosen for the framing due to it's high strength to density ratio. For insulation, a less dense foam coated in mylar was used to maintain PeaPod's insulating capabilities while reducing mass.

The following are over-estimates:

Frame and Trays: \textbf{54kg} (4.5kg per frame unit)
Insulation: \textbf{5kg}
Control Module: \textbf{10kg}

\subsection{Crew Time Estimate}
\label{app:crewtime}

Setup: Before plants are grown, crews must make sure solution containers are full, and UV sterilize the housing.

Harvesting: Crew members simply need to remove the trays from the unit to access the grow trays. This largely depends on the plant type, ranging from 5 minutes (picking fruit) to 15 minutes (harvesting root vegetables).

Output processing and storage: Processing will depend on the produce grown and desired end product, varying from boiling to frying to baking etc. average 30 minutes per meal.

\subsection{Optimization Method}
\label{app:optimization}

A common existing approach to plant optimization in academia is to have a simple neural network train on a dataset of \textbf{fixed/unchanging} environment parameters (input) and \textbf{final} plant metrics (output). This approach is severely limited, in that it does not account for changes over time. Environment parameters cannot be changed, and as such cannot target specific plant growth phases (i.e. specific lighting and nutrients for germination vs vegetation vs fruiting). In addition, the exclusion of plant metrics throughout the duration of plant growth means that a system has no way to respond to failing plant health, as it has no data for this.

Instead, a statistical model is trained on an ordinary differential representation of plant behaviour and phenology, which takes into account the cumulative property of growth: A plant's current state is not \textit{immediately} related to it's surrounding environment (consider a "flash-freeze" step change - the plant would not immediately die if nominal temperature was resumed), but instead a plant's state's rate of change (i.e growth rate and other processes) depend on both its internal state and the current environment state.

Assume a plant's growth rate (or "state change") is related to its current internal state $\vec P \in \R^n$ (for $n$ plant metrics) and the environment conditions $\vec E \in \R^m$ (for $m$ environment parameters). Let these both be functions $\vec P (t),\vec E(t)$ defined at each point in time $t$, where $t=0$ indicates the time of planting. Assume that this relationship is constant for all members of a given species.

Define plant state change $\vec P'$: 

$$\vec P'(t) = \frac{d}{dt}\vec P(t)$$

Define the plant-environment phenology mapping function $Q$, a re-definition of the state change in terms of plant and environment states: 

$$Q(\vec P(t), \vec E(t))=\vec P'(t)$$ 

Given the internal and external state changes, determine the plant's state change across time:

\begin{enumerate}
    \item Set $\vec E_{set}(t)$ for each point in time, aka the program;
    \item Record and smooth/filter $\vec P(t)$ (plant metrics) and $\vec E(t)\approx \vec E_{set}(t)$ (environment sensors) for each point in time;
    \item Calculate $\vec P'(t)$ from $\vec P(t)$ for each point in time;
    \item Fit $Q$ via a statistical or machine learning model, $Q_{model}$, using $\vec P(t),\vec E(t)$ (input) and $\vec P'$ (output) at each point in time as our dataset;
\end{enumerate}

The optimal form of $Q_{model}$ is an ongoing topic of investigation.

By fitting $Q$ as $Q_{model}$, we can predict $\vec P$ at any point in time for any program $\vec E$. For example:

$$\vec P(t_f)=\int_0^{t_f}Q_{model}(\vec P(t),\vec E(t))~dt~~~~\text{or a numerical method}$$

\end{spacing}

\newpage

% References
\bibliographystyle{IEEEtran}
\bibliography{references}
\end{document}