PeaPod is a modular, automated plant growth environment and distributed research tool. It can generate any environment for any crop, while collecting plant growth data for optimization.

The growth environment is adaptable to many plants and mission requirements. It consists of "unit cell" cubes that can be joined upwards and sideways to increase space. It is insulated with internally-reflective panels for efficiency.

PeaPod uses automated control systems to generate desired environments. These are air thermoregulation, humidity control, LED lighting, and an aeroponics system. They are automated by an onboard computer and housed in a "control module" at the top of the unit. This lets power be "multiplied" for extended PeaPods by adding more control modules in a controller-follower topology.

Plant growth cups and lighting platforms are built on modular "trays" mounted to the inside of the housing so the user can position plants and lights to accommodate any plant size.

Throughout a growth cycle, all environment parameters and growth metrics are collected. This data trains a statistical ML model to represent the plant's phenology over time in the environment. The output function can then be optimized for yield mass, nutrient concentration, flavour, resource efficiency, or any other metric.

Combining these into an accessible open-source design, PeaPod provides unrivalled versatility and reliability to food production systems both terrestrially and on long-duration space missions.