\subsection{Gas Composition Regulation and Exchange}
\label{sec:gas}

\textbf{Purpose}: Controls gas composition of the growth environment by mediating exchange with surroundings.

\textbf{Function}:
\begin{itemize}
    \item \textbf{Inputs}: Power, exchange control signal (open/closed and exchange rate)
    \item \textbf{Outputs}: Gas intake (from surroundings), gas exhaust (to surroundings; filtered and humidity-controlled)
\end{itemize}

\textbf{Method}:
\begin{enumerate}
    \item \textit{Setup}:
    \begin{enumerate}
        \item Connect exhaust port to onboard filtration/dehumidification system;
        \item Connect shutter servos, fans to control module;
    \end{enumerate}
    \item \textit{Testing}:
    \begin{itemize}
        \item Shutter servos, fans operate as intended;
        \item Ports are air-tight when closed;
        \item Exhaust filter removes all aerosols (i.e. pollen, seeds) and pathogens;
        \item Exhaust dehumidification brings humidity down to ambient (60\% on ISS); % TODO: Source?
    \end{itemize}
    \item \textit{Process}:
    \begin{enumerate}
        \item On-demand, intake and exhaust ports activate. Shutters open, and fans are enabled;
        \item Intake port draws in air from surroundings;
        \item Exhaust port expels air through filtration and dehumidification systems to be recycled;
    \end{enumerate}
    \item \textit{Shutdown}:
    \begin{enumerate}
        \item Disconnect exhaust port from filtration/dehumidification system;
        \item Disconnect shutter servos, fans from control module;
    \end{enumerate}
\end{enumerate}

\textbf{Features}:
\begin{itemize}
    \item \textit{Exchange Port}: Intake and exhaust, normally-sealed. Each comprises:
    \begin{itemize}
        \item \textit{Shutters}: Servo-actuated shutters enable opening and closing of ports on demand. Air-tight when closed.
        \item \textit{Fan}: Humidity-rated fans control gas intake and exhaust rates.
        \item \textit{Filter}: Polyethylene-polyropylene blend (non-toxic) MERV 13 (0.3 micron) air filters \cite{filter} eliminate risk of any airborne pathogens being transferred into or out of the system during gas exchange.
    \end{itemize}
    \item \textit{Gas Concentration Sensors}: Collects data on concentrations (ppm) of relevant gasses (CO${}_2$, O${}_2$, etc.). Reports to automation (\ref{sec:automation}).
    \item \textit{Output Dehumidifier}: \textbf{Onboard life support systems} provides a dehumidifier (as well as additional filtration) to mitigate exhaust humidity.
\end{itemize}