\subsection{Lighting}
\label{sec:lighting}

\textbf{Purpose}: Provide all necessary light for plant growth.

\textbf{Function}:
\begin{itemize}
    \item \textbf{Inputs}: Power, lighting spectrum-intensity distribution control signal (aka per-LED modulation signals)
    \item \textbf{Outputs}: Light
\end{itemize}

\textbf{Method}:
\begin{enumerate}
    \item \textit{Setup}:
    \begin{enumerate}
        \item Connect power and spectrum-intensity distribution control signal to driver board;
        \item Mount driver board and many LED boards to lighting tray;
        \item Daisy-chain LED boards, connect first and last to driver board;
    \end{enumerate}
    \item \textit{Testing}:
    \begin{itemize}
        \item Spectrum-intensity distribution control signal modulates LED power as expected;
        \item Passive heat sinks dissipate enough heat;
    \end{itemize}
    \item \textit{Process}:
    \begin{enumerate}
        \item Power is delivered to drivers;
        \item Control signals "dim" drivers to modulate intensity distribution across spectrum;
        \item Power drivers power lights;
        \item Lights emit light;
    \end{enumerate}
    \item \textit{Shutdown}:
    \begin{enumerate}
        \item Disconnect power and signals;
        \item Disconnect and dismount boards;
    \end{enumerate}
\end{enumerate}

\textbf{Features}:
\begin{itemize}
    \item \textit{LED Lights}: LEDs offer high power output, less heat, and precise wavelengths while minimizing risk of damaging plant tissues. Many "series" (wavelengths) enable wide and fine control of intensity-spectrum distribution, with a focus on Photosynthetically-Active Radiation (PAR)\footnote{\textit{NOTE}: This system is modifiable to use other lights (i.e. Near-UV)}. Located across multiple smaller daisy-chained PCBs to minimize cost. LED series include:
    \begin{itemize}
        \item Royal Blue
        \item Cool White
        \item Warm White
        \item Photo Red
        \item Far Red (Near-IR)
    \end{itemize}
    \item \textit{LED Power Drivers}: Constant-current PWM-dimmable DC-DC buck converters, specialized for LEDs. One per series, driving a set of LEDs. Located on a separate PCB (one per lighting tray).
    \item \textit{Heat Sink}: Passive (fan-less) cooling solution for LEDs. Mounted to opposing face of PCB.
\end{itemize}