\subsection{Air Humidification}
\label{sec:airhum}

\textbf{Purpose}: Actively \textit{increases} growth environment air humidity.

\textbf{Function}:
\begin{itemize}
    \item \textbf{Inputs}: Power, humidification on/off control signal (\ref{sec:automation}), RO water\footnote{RO water contains no minerals/particulate, and as such prevents the common problem of mesh clog/calcification.};
    \item \textbf{Outputs}: Water vapour, humidity sensor signal;
\end{itemize}

\textbf{Method}:
\begin{enumerate}
    \item \textit{Setup}:
    \begin{enumerate}
        \item Connect humidification control signal to control module;
        \item Connect humidity sensor signal to control module;
        \item Connect RO water line to water tank;
    \end{enumerate}
    \item \textit{Testing}:
    \begin{itemize}
        \item Humidification unit responds to control signal as expected;
        \item Humidity sensor reads as expected;
        \item Tank does not leak;
    \end{itemize}
    \item \textit{Process}:
    \begin{enumerate}
        \item Water is delivered to a small tank (nebulizer is mounted);
        \item Power and control signal activate a nebulizer driver;
        \item Nebulizer vapourizes water;
    \end{enumerate}
    \item \textit{Shutdown}:
    \begin{enumerate}
        \item Disconnect RO water line and drain tank;
        \item Disconnect humidification control signal and humidity sensor signal from control module;
    \end{enumerate}
\end{enumerate}

\textbf{Features}:
\begin{itemize}
    \item \textit{Circulation Fans}: See Section \ref{sec:airthermoregulation}.
    \item \textit{Humidity Sensor}: Located throughout the growth environment to measure air humidity. Informs a \textbf{bang-bang} control loop (\ref{sec:automation});
    \item \textit{Humidification Unit}: Easily controllable and produces a consistent vapour. Comprised of:
    \begin{itemize}
        \item \textit{Water Tank}: Holds a small amount of water behind the piezoelectric mesh.
        \item \textit{Piezoelectric Mesh Disc}: Oscillates in such a way that vapour is generated when water is passed over it. Mounted to the water tank.
        \item \textit{Driver Circuit}: Fixed-frequency\footnote{113kHz for 20mm disc} 555 timer circuit driving an amplifier/LC circuit generates an AC signal. Powers the piezoelectric disc.
    \end{itemize}
\end{itemize}